Assessing the Accessibility of Protein Tunnels using Motion Planning

### 2017-12-08 paper.tex
time/distance graphs images updated by A_1*

\begin{table}[ht]
\centering
\caption{\label{tab::selection}
    \small
    The influence of the conformation selection method to the traversability rates in the first tunnel.
    The number after~`$/$' denotes the number of atoms.
}
\small
\renewcommand{\tabcolsep}{4.3pt}
{\scriptsize
\renewcommand{\arraystretch}{0.7}
\input graphSel.tex
}
\end{table}

@@

%originally last two paragraphs in the experiment section, for resubmition, they are moved here to discussion
The proposed \RA\ planner provides higher traversability rate than RRT-Retraction (\RB).
The distances of the configuration trees (measured using the 3D Euclidean metric) to the active site and the runtimes in each frame
are shown in Fig.~\ref{fig::comparison}.
The runtimes of both algorithms increase in those frames, where the tunnel is not traversable, i.e., where the distance
to the active site is more than 2~\AA\ (for example, in the frame no. 60).
The comparison between \RA\ and \RC\ shows that utilization of the  atom-based metric (used in \RA) leads to higher traversability rate
in the case of large scales and larger ligands (e.g., m056 with $\smin=0.8$: 15~\% with the metric, but to only 6~\% without it).
On the other hand, there is not practical difference between \RA\ and \RC\ in the case of more scaled-down ligands.

@@

{\def\a{270}
\begin{figure}[t]
\centering
%\includegraphics[width=0.17\textwidth,angle=\a]{fig/m037tmins-03tunnel-1rrt_path_time-2}
%\includegraphics[width=0.17\textwidth,angle=\a]{fig/m037tmins-03tunnel-1trajDistToGoal-2}
\includegraphics[width=0.18\textwidth,angle=\a]{fig/crop1}
\includegraphics[width=0.18\textwidth,angle=\a]{fig/crop2}
\caption{\label{fig::comparison}
    \small
    Runtimes and the distance to the active site for the m037 ligand at scale 0.6.
    The values are computed from all 200 trials (20 initial configurations $\times$ 10 trials).
    Only each third frame is shown in the graph.
}
\end{figure}
}

>>>>

\begin{table}[ht]
\centering
\caption{\label{tab::selection}
    \small
    The influence of the conformation selection method on the traversability rates in the first (main) tunnel.
    The number after~`$/$' denotes the number of atoms.
}
\small
\renewcommand{\tabcolsep}{4.3pt}
{\scriptsize
\renewcommand{\arraystretch}{0.7}
\input graphSel.tex
}
\end{table}

@@

%originally last two paragraphs in the experiment section, for resubmition, they are moved here to discussion
The proposed \RA\ planner provides higher traversability rate than RRT-Retraction (\RB).
The distances of the configuration trees (measured using the 3D Euclidean metric) to the active site and the runtimes in each frame
are shown in Fig.~\ref{fig::comparison}.
The runtimes of both algorithms increase in those frames, where the tunnel is not traversable, i.e., where the distance
to the active site is more than 2~\AA\ (for example, in the frame no. 60).
The comparison between \RA\ and \RC\ shows that utilization of the  atom-based metric (used in \RA) leads to higher traversability rate
in the case of large scales and larger ligands (e.g., m056 with $\smin=0.8$: 15~\% with the metric, but to only 6~\% without it).
Both \RA\ and \RC\ provided trajectories with the same traversability rate in the case of lower scales ($\smin<0.6$).

@@

{\def\a{0}
\begin{figure}[t]
\centering
%\includegraphics[width=0.17\textwidth,angle=\a]{fig/m037tmins-03tunnel-1rrt_path_time-2}
%\includegraphics[width=0.17\textwidth,angle=\a]{fig/m037tmins-03tunnel-1trajDistToGoal-2}
\includegraphics[width=0.2\textwidth,angle=\a]{fig/crop1}
\includegraphics[width=0.2\textwidth,angle=\a]{fig/crop2}
\caption{\label{fig::comparison}
    \small
    Runtimes and the distance to the active site for the m037 ligand at scale 0.7.
    The values are computed from all 200 trials (20 initial configurations $\times$ 10 trials).
    Only each third frame is shown in the graph.
}
\end{figure}
}
